Effective Vaccination Strategies for an H1N1 Epidemic in Ithaca, New York

### 2015-10-01 final_submission/manuscript.tex
I'm done

            0.0263    7.4504    3.3864    0.1356
    \end{lstlisting}
    Running this with vaccine distributions (.1, .4, .4, .1) and $\mu = \mu * 20$results in the following MATLAB output:

@@

    Running this with vaccine distributions (.4, .1, .1, .4) and $\mu = \mu * 20$results in the following MATLAB output:

@@

            0.0263    7.4485    3.3857    0.1356
    \end{lstlisting}
% \subsection{Analysis of Model (robustness)}
% 	//TODO
% \subsection{Strengths and Weaknesses}
% 	//TODO
% \subsection{Future Work}
% 	//TODO

>>>>

            0.0263    7.4504    3.3864    0.1356
    \end{lstlisting}
    Running this with vaccine distributions (.1, .4, .4, .1) and $\mu = \mu * 20$ results in the following MATLAB output:

@@

    Running this with vaccine distributions (.4, .1, .1, .4) and $\mu = \mu * 20$ results in the following MATLAB output:

@@

            0.0263    7.4485    3.3857    0.1356
    \end{lstlisting}
    \subsection{Analysis of Model}
	 This model suffer from being dependent upon too many parameters, and it is hard to come up with an optimal vaccine distribution. Tweaking the parameters a little bit can have a drastic effect on the model, and it relies too much on our research being accurate. In the future I would search for a pareto optimal distribution. Also, I would fix the assumption of a linear vaccination rate so we are not wasting vaccines on a completely vaccinated population, and can test getting all infants out of the way at the beginning.
% \subsection{Strengths and Weaknesses}
% 	//TODO
% \subsection{Future Work}
% 	//TODO
